### 2013-03-28 doc/sosp13/evaluation.tex
Write a bit about why GUPS is interesting.

\subsection{Basic \Grappa Mechanisms}
\label{eval:basic}

@@

\paragraph{Global memory and communication.} We measure the performance of
\Grappa's global memory and communication layers using a faithful
implementation of the giga updates per second (GUPS) benchmark.
Read-modify-write updates are dispatched at random to a large array. This
benchmark stresses the communication layer of \Grappa separately from the
scheduler, because only a single worker is used per system node.
Figure~\ref{fig:grappa-gups} shows that \Grappa is able to sustain well over a
billion updates per second with 64 nodes. This compares very favorably to
published results~\cite{gups} for other high-end HPC systems.

\begin{figure}[ht]
    \begin{center}
      \includegraphics[width=0.5\textwidth]{results/gups/gups.pdf}
    \end{center}
    \caption{GUPS (giga updates per second) for \Grappa as the number of nodes grows.}
    \label{fig:grappa-gups}
\end{figure}

>>>>

\subsection{Basic \Grappa Performance}
\label{eval:basic}

@@

\paragraph{Global memory and communication.} We measure the performance of
\Grappa's global memory and communication layers using a faithful
implementation of the giga updates per second (GUPS) benchmark.
Read-modify-write updates are dispatched at random to a large array. This
benchmark stresses the communication layer of \Grappa separately from the
scheduler, because only a single worker is used per system node.
Figure~\ref{fig:grappa-gups} shows that \Grappa is able to sustain well over a
billion updates per second with 64 nodes.

This compares very favorably to
published results~\cite{gups} for other high-end HPC systems.
Though the actual computation done by GUPS is completely non-sensical, irregular, data-intensive applications typically must be able to sustain a high rate of random accesses in order to, for example, visit and mark vertices during a graph traversal. High random access rate in a distributed setting has been a long-standing challenge in HPC.

\begin{figure}[ht]
    \begin{center}
      \includegraphics[width=0.5\textwidth]{figs/gups.pdf}
    \end{center}
    \caption{GUPS (giga updates per second) for \Grappa as the number of nodes grows.}
    \label{fig:grappa-gups}
\end{figure}
